---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```

<h1><code>snomedizer</code>: R Interface to the SNOMED CT Terminology Server REST API</h1>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/ramses-antibiotics/snomedizer.svg?branch=master)](https://travis-ci.org/ramses-antibiotics/snomedizer)
[![Codecov test coverage](https://codecov.io/gh/ramses-antibiotics/snomedizer/branch/master/graph/badge.svg)](https://codecov.io/gh/ramses-antibiotics/snomedizer?branch=master)
<!-- badges: end -->

<p class="lead">
<code>snomedizer</code> is an R package to manipulate the SNOMED clinical ontology using the 
   SNOMED CT Terminology Server REST API <https://github.com/IHTSDO/snowstorm>.
</p>

## Installation

<!-- 
You can install the released version of snomedizer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("snomedizer")
```
-->

You can install the development version from [GitHub](https://github.com/ramses-antibiotics/snomedizer) with:

``` r
install.packages("devtools")
devtools::install_github("ramses-antibiotics/snomedizer")
```
## Example

`snomedizer` provides a direct interface to the SNOMED CT Terminology Server REST API. 

By default, the package uses the official [IHTSDO API endpoint](https://browser.ihtsdotools.org/snowstorm/snomed-ct/), subject to the [SNOMED International SNOMED CT Browser License Agreement](https://browser.ihtsdotools.org/) (restricted to reference purposes).

For example, \code{[GET /branch/concepts](https://snowstorm.ihtsdotools.org/snowstorm/snomed-ct/swagger-ui.html#!/Concepts/findConceptsUsingGET)} is implemented in `api_concepts()`:

```{r api_concepts_pneumonia}
library(snomedizer)
api_concepts(term = "pneumonia", activeFilter = TRUE)
```

Simpler wrapper functions are available for common operations, which provide results as data frames:

```{r concepts_find_pneumonia, warning=TRUE}
concepts_find(term = "pneumonia", limit = 5) %>% 
  dplyr::select(conceptId, fsn.term, pt.term) 
```

## Code of conduct

The `snomedizer` project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).

By contributing to this project, you agree to abide by its terms.
